---
title: "Report test"
author: "jmfti"
date: "2022-09-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages(c("ggplot2", "dplyr"))
library(ggplot2)
library(dplyr)
```

# Report

This is only a test, a Proof of Concept. The data should be taken from a stable, a stationary interval time. Not the ramp-up. So  do not consider this as a correct approach. Data must be classified between ramp-up stage and stable stage. A k6 tag should work.

```{r, echo=FALSE}
base_path <- "/report/output"
#base_path <- "c:/temp/demoqabook/output"
#filename <- "C:/temp/demoqabook/output/2022_09_21_09_51_30_results.csv"
filename <- sprintf("%s/baseline.csv", base_path)
df <- read.csv(filename)
df$time <- as.POSIXct(df$timestamp, origin="1970-01-01")
#head(df)

#summary(df)

req_durations <- df[df$metric_name == "http_req_duration",]
req_sending <- df[df$metric_name == "http_req_sending",]
req_failed <- df[df$metric_name == "http_req_failed",]

group_durations <- df[df$metric_name == "group_duration",]
```

## Response times distribution by groups

```{r, echo=FALSE}

ggplot(req_durations) +
  aes(x = "", y = metric_value, fill = group) +
  geom_violin(adjust = 1L, scale = "area") +
  scale_fill_brewer(palette = "Dark2", direction = 1) +
  labs(x = "actions", y = "ms") +
  theme_minimal()
```

## Number of requests sending
Must fix: aggregate by sec

```{r, echo=FALSE}

ggplot(req_sending) +
  aes(x = time, y = metric_value) +
  geom_line(size = 0.5, colour = "#112446") +
  theme_minimal() +
  facet_wrap(vars(group))

# number of errors
errors <- df %>% filter(metric_name == "http_req_failed") %>% select(metric_value, group) %>% 
  group_by(group) %>% summarize(sum_errors = sum(metric_value, na.rm=TRUE))
errors

sent <- df %>% filter(metric_name == "http_req_sending") %>% select(time, metric_value, group) %>% group_by(time, group) %>% summarize(req_min=sum(metric_value) * 60)

ggplot(sent, aes(x=time)) + geom_line(aes(y=req_min, col=group)) + theme_minimal()
```

# Results comparison
## Requests duration by group on baseline

```{r, echo=FALSE}
# baseline
print(sprintf("%s/baseline.csv", base_path))
bldf <- read.csv(filename)
# current run
crdf <- read.csv(sprintf("%s/result_current_run.csv", base_path))

bldf$time <- as.POSIXct(bldf$timestamp, origin="1970-01-01")
crdf$time <- as.POSIXct(crdf$timestamp, origin="1970-01-01")

bldf %>% filter(metric_name == "http_req_duration") %>% select(metric_value, group) %>% group_by(group) %>% summarize(response_time = mean(metric_value))

bldf %>%
 filter(metric_name %in% "http_req_duration") %>%
 ggplot() +
  aes(x = "", y = metric_value, fill = group) +
  geom_violin(adjust = 1L, scale = "area") +
  scale_fill_hue(direction = 1) +
  theme_minimal()

```

## Requests duration by group on current run

```{r, echo=FALSE}
crdf %>% filter(metric_name == "http_req_duration") %>% select(metric_value, group) %>% group_by(group) %>% summarize(response_time = mean(metric_value))

crdf %>%
 filter(metric_name %in% "http_req_duration") %>%
 ggplot() +
  aes(x = "", y = metric_value, fill = group) +
  geom_violin(adjust = 1L, scale = "area") +
  scale_fill_hue(direction = 1) +
  theme_minimal()

```


